---
title: "dev_history.Rmd for working package"
author: "Sébastien Rochette"
date: "23/01/2021"
output: html_document
---

```{r development, include=FALSE}
library(testthat)
```

<!--
# Description of your package

This will fill the description of your package.
Add this chunk using `fusen::description_chunk()`
--> 

```{r description}
# Describe your package

fusen::fill_description(
  fields = list(
    Title = "R Wrapper for YAP",
    Description = "Simple R wrapper for working with YAP.",
    `Authors@R` = c(
      person("Almog", "Simchon", email = "almog.si@gmail.com", role = c("aut", "cre"), comment = c(ORCID = "0000-0003-2629-2913"))
    )
  )
)
# Define License with use_*_license()
usethis::use_mit_license("Almog Simchon")
```

# Calculate the median of a vector

```{r function}
#' Yap
#'
#' @param x Text of type Character
#' @param token Your YAP API token
#' @inheritParams stats::median
#'
#' @return
#' List of YAP output
#' @export
#'
#' @examples

yap <- function(x, token){
  
  Token <- token
  text  <-  x 
  verb<-"POST"
  headers <- c(
    'Content-Type' = "application/json"
  )
  
  data<-paste0('{"data": ','"',text,'"}')
  cat(data)
  url <- paste0('https://www.langndata.com/api/heb_parser?token=',Token)
  
  response  <- httr::VERB(verb=verb,
                          url = url,
                          body=data,
                          httr::add_headers(
                            headers
                            
                          )
  )
  
  if (response$status_code==200){
    a<-httr::content(response)
    return(a)
  }
  else{
    return ("API error")
  }
}
```

# Calculate the mean of a vector
## Use sub-functions in the same chunk

```{r function-1}
#' Lemmas
#'
#' @param x List of YAP output
#'
#' @return
#' Lemma form of text x
#' @export 
#'
#' @examples
yap_lemmas <- function(x){
  return(strsplit(x$lemmas, split = " ", )[[1]])
}
```

```{r examples-1}
text <- "גנן גידל דגן בגן"
token <- "af0e7a2f98f7e43872593bfc2f2ff580"
yap_list <- yap(text, token)
yap_lemmas(yap_list)
```

```{r function-2}
#' Lemmas
#'
#' @param x List of YAP output
#'
#' @return
#' Tibble CoNLL dependency tree 
#'
#' @import dplyr, tibble
#'
#' @export 
#'
#' @examples
dep_conll <- function(x){
  tbl <- tibble::as_tibble(t(tibble::as_tibble(x$dep_tree)), .name_repair = "minimal")
  names(tbl) <- tolower(c("ID", "FORM", "LEMMA", "CPOSTAG", "POSTAG",
                          "FEATS", "HEAD", "DEPREL", "PHEAD", "PDEPREL"))
  return(tbl %>% 
           dplyr::mutate(dplyr::across(dplyr::everything(), unlist)))
}
```

```{r examples-2}
text <- "גנן גידל דגן בגן"
token <- "af0e7a2f98f7e43872593bfc2f2ff580"
yap_list <- yap(text, token)
dep_conll(yap_list)
```

```{r function-3}
#' Lemmas
#'
#' @param x List of YAP output
#'
#' @return
#' Tibble Lattice dependency tree 
#'
#' @import dplyr, tibble
#'
#' @export
#'
#' @examples
dep_lattice <- function(x){
  tbl <- tibble::as_tibble(t(tibble::as_tibble(x$md_lattice)), .name_repair = "minimal")
  names(tbl) <- tolower(c("empty", "gen",
                          "lemma", "num",
                          "num_2", "num_last",
                          "num_s_p", "per", "pos", "pos_2",
                          "tense", "word"))
  return(tbl %>% 
           dplyr::mutate(dplyr::across(dplyr::everything(), unlist)))
}
```

```{r examples-3}
text <- "גנן גידל דגן בגן"
token <- "xxx"
yap_list <- yap(text, token)
dep_lattice(yap_list)
```
# There can be development actions

These will be included in the `dev_history.R` file of your package, but won't be direct part of it.

```{r development-1, eval=FALSE}
# Run but keep eval=FALSE to avoid infinite loop
# Execute in the console directly
fusen::inflate(rmd = "dev/dev_history.Rmd")
```


# Inflate your package

You're one inflate from paper to box.
Build your package from this very Rmarkdown using `fusen::inflate()`

- Verify your `"DESCRIPTION"` file has been updated
- Verify your function is in `"R/"` directory
- Verify your test is in `"tests/testthat/"` directory
- Verify this Rmd appears in `"vignettes/"` directory
