---
title: "exploration"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{exploration}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(yappr)
```

<!--

# Description of your package

This will fill the description of your package.
Add this chunk using `fusen::description_chunk()`
--> 


# Use YAP

# Extract Lemmas

```{r examples-1}
text <- "גנן גידל דגן בגן"
token <- "YourAPIToken"
yap_list <- yap(text, token)
yap_lemmas(yap_list)
```

```{r examples-2}
text <- "גנן גידל דגן בגן"
token <- "YourAPIToken"
yap_list <- yap(text, token)
dep_conll(yap_list)
```

```{r examples-3}
text <- "גנן גידל דגן בגן"
token <- "YourAPIToken"
yap_list <- yap(text, token)
dep_lattice(yap_list)
```

# There can be development actions

These will be included in the `dev_history.R` file of your package, but won't be direct part of it.


# Inflate your package

You're one inflate from paper to box.
Build your package from this very Rmarkdown using `fusen::inflate()`

- Verify your `"DESCRIPTION"` file has been updated
- Verify your function is in `"R/"` directory
- Verify your test is in `"tests/testthat/"` directory
- Verify this Rmd appears in `"vignettes/"` directory

