---
title: "Hebrew NLP with YAP in the quanteda workflow"
output: rmarkdown::html_vignette
vignette: >
  %\\VignetteIndexEntry{Hebrew NLP with YAP in the quanteda workflow}
  %\\VignetteEngine{knitr::rmarkdown}
  %\\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment  = "#>",
  eval     = FALSE
)
```

## Why this package exists

Hebrew is a morphologically rich language: a single orthographic word can
package several morphemes (definite article, prepositions, pronominal
suffixes, etc.). Most R text-analysis pipelines assume English-shaped tokens,
which means bag-of-words on raw Hebrew tokens gives you a matrix dominated by
inflectional variants of the same lemma.

[YAP](https://github.com/OnlpLab/yap) (Yet Another Parser) is the open-source
morphological analyzer, disambiguator, and dependency parser for Hebrew.
`yappr` wraps it so you can call it from R and feed the result into
[`quanteda`](https://quanteda.io) the same way you\'d use `spacyr` for English.

## Installation

See the README for the full install (Windows users need WSL).

## The flow

```{r}
library(yappr)
library(quanteda)

texts <- c(
  doc1 = "\u05D4\u05D9\u05DC\u05D3\u05D9\u05DD \u05D4\u05DC\u05DB\u05D5 \u05DC\u05D1\u05D9\u05EA \u05D4\u05E1\u05E4\u05E8.",
  doc2 = "\u05D4\u05D9\u05D5\u05DD \u05D9\u05D5\u05DD \u05D9\u05E4\u05D4 \u05D5\u05D0\u05E0\u05D7\u05E0\u05D5 \u05E9\u05DE\u05D7\u05D9\u05DD."
)

parsed <- yap_parse(texts, dependency = TRUE)
parsed
```

Each row is a **morpheme**, not an orthographic token. `token_id` is 1..n
within each sentence; `sentence_id` is 1..m within each document.

## Lemmatized DFM in one call

```{r}
# Hebrew-aware pipeline: lemma + content POS + stopwords + punct strip
d <- yap_to_dfm(texts, heb_lemma = TRUE)
topfeatures(d, 10)
```

Turn off individual pieces as needed:

```{r}
yap_to_dfm(texts,
           heb_lemma = TRUE,
           remove_stopwords = FALSE,          # keep function words
           pos_keep = c("NN","VB"))           # nouns + verbs only
```

## Using dependency parses

With `dependency = TRUE`, the parsed data frame carries `head_token_id` and
`deprel`. Ordinary tabular data \u2014 anything you can do with `dplyr`, you can
do here:

```{r}
subset(parsed, deprel == "subj",
       select = c(doc_id, sentence_id, token, lemma))
```
